---
title: "What should I eat for dinner?"
author: "Sarah Shy"
date: "12/31/2020"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  fig.width = 3,
  fig.height = 2
)
```

## Introduction

Using the Yelp API, I pulled data on 50 restaurants in the State College area. This is an exploratory analysis of the restaurant ratings.

```{r, frontMatter}
library(tidyverse)
library(httr)
library(readr)
library(ggplot2)
library(ggmap)
library(magrittr)
library(plotly)
library(scales)
library(viridis)
library(kableExtra)
```


```{r, api}
client_id <- read_file("yelp_api_id.txt")
client_secret <- read_file("yelp_api_key.txt")

res <- POST("https://api.yelp.com/oauth2/token",
            body = list(grant_type = "client_credentials",
                        client_id = client_id,
                        client_secret = client_secret))

token <- content(res)$access_token
```

```{r, getData}
yelp <- "https://api.yelp.com"
term <- "food"
location <- "State College, PA"
categories <- NULL
limit <- 50
radius <- 2000
url <- modify_url(yelp, path = c("v3", "businesses", "search"),
                  query = list(term = term, location = location, 
                               limit = limit,
                               radius = radius))
res <- GET(url, add_headers('Authorization' = paste("bearer", client_secret)))

results <- content(res)



yelp_httr_parse <- function(x) {

  parse_list <- list(id = x$id, 
                     name = x$name, 
                     rating = x$rating, 
                     review_count = x$review_count, 
                     latitude = x$coordinates$latitude, 
                     longitude = x$coordinates$longitude, 
                     address1 = x$location$address1, 
                     city = x$location$city, 
                     state = x$location$state, 
                     distance = x$distance)
  
  parse_list <- lapply(parse_list, FUN = function(x) ifelse(is.null(x), "", x))
  
  df <- tibble(id=parse_list$id,
                   name=parse_list$name, 
                   rating = parse_list$rating, 
                   review_count = parse_list$review_count, 
                   latitude=parse_list$latitude, 
                   longitude = parse_list$longitude, 
                   address1 = parse_list$address1, 
                   city = parse_list$city, 
                   state = parse_list$state, 
                   distance= parse_list$distance)
  df
}

results_list <- lapply(results$businesses, FUN = yelp_httr_parse)

restaurants <- do.call("rbind", results_list)
```


## Overview of food-related business

Variables:
```{r}
names(restaurants)
```

## Overall Ratings:
```{r}
summary(restaurants$rating)

ggplot(restaurants, aes(x = rating)) +
  geom_boxplot(fill = "orange") +
  theme_minimal()
ggplot(restaurants, aes(x = rating)) +
  geom_histogram(binwidth = 1, fill = "orange", col = "black", boundary = 0) +
  xlim(0,5) +
  theme_minimal()
```

At first glance, it seems people generally enjoy the restaurants, with a median rating of 4 stars, and none below 2.5.

However, we have not taken into account the number of reviews that these restaurants received.

## Number of Reviews
```{r, fig.width = 3, fig.height = 4}
summary(restaurants$review_count)

restaurants %>%
  filter(review_count <= 5) %>%
  select(name, review_count) %>%
  kable() %>%
  kable_styling()
```

The median number of reviews is 47.5. There is one restaurant with only one review, Yallah Taco (the new location on W. College Ave). There are 3 other restaurants with 5 reviews or fewer: Cafe Alina, Central Reseration, and Hello Bistro. I note that all 4 restaurants are relatively new, having opened in the last year to year and a half.

```{r}
restaurants %>%
  arrange(desc(review_count)) %>%
  select(name, review_count) %>%
  head(3) %>%
  kable() %>%
  kable_styling()
```

Faccia Luna, Little Szechuan, and Big Bowl Noodles are the most frequently reviewd restaurants.


## Ratings and Number of Reviews
```{r}
ggplot(restaurants, aes(x = review_count, y = rating)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Number of reviews")
```

The scatterplot indicates no relationship between the number of reviews and the overall restaurant rating. There is a weak correlation between the two variables, r=`rcor(restaurants$review_count, restaurants$rating)`.

## Top Restaurants

The 6 most highly rated restaurants are:
```{r}
restaurants %>%
  arrange(desc(rating)) %>%
  select(name, rating, review_count) %>%
  head %>%
  kable() %>%
  kable_styling()
```

The top-rated restaurant in State College is Cafe Alina with a bangin' 5 star rating. However, since Cafe Alina only has 2 reviews, the rating we see may not be representative of the true customer experience. The two customers who reviewed may have had a particularly enjoyable experience at the restaurant and felt compelled to share their amazing experience.

## Bottom Restaurants

The 6 most poorly rated restaurants are:
```{r}
restaurants %>%
  arrange(rating) %>%
  select(name, rating, review_count) %>%
  head %>%
  kable() %>%
  kable_styling()
```

We see that Weirdough, which opened just this past September, is off to a rough start. Uncle Chen's Mongolian is tied for last place in the ratings.

## Map of restaurants

You may use the interactive maps to explore the locations of the restaurants in the dataset. In the first plot, the restaurants are colored by their Yelp rating. In the second plot, the restaurants are colored by whether or not their Yelp rating is above the median rating in the dataset (4.0).

```{r}
# set API key
register_google(key = read_file("google_api_key.txt")) 

# get map
sc_map <- get_map(location = c(lon = mean(restaurants$longitude),
                               lat = mean(restaurants$latitude)), zoom = 14,
                  maptype = "roadmap", scale = 2)

```

```{r, fig.width = 7, fig.height = 6}
# plot restaurants
map_rating <- ggmap(sc_map) +
  geom_point(data = restaurants, aes(x = longitude, y = latitude, col = rating, group = name), alpha = 0.8) +
  scale_color_viridis(direction = -1) +
  labs(x = "", y = "")

ggplotly(map_rating, tooltip = "group")


restaurants %<>% mutate(top_half = ifelse(rating >= median(rating), "Above median", "Below median"))
map_top_half <- ggmap(sc_map) +
  geom_point(data = restaurants, aes(x = longitude, y = latitude, col = top_half, group = name), alpha = 0.5) +
  scale_color_manual(values = c("blue", "red")) +
  labs(x = "", y = "", col = "Rating")

ggplotly(map_top_half, tooltip = "group")
```






